Symbolic Weighted Language Models and\\ Parsing over Infinite Alphabets

### 2021-09-02 FST-TCS/rebuttal/rebuttal-reviews.md

----------- Overall evaluation -----------
The paper introduces symbolic weighted automata (swA) as a generalization of finite automata in two directions: first, like symbolic automata, they allow infinite input alphabets and second, like weighted automata, they map each input word to a value in a semiring .  In the same spirit, symbolic weighted transducers (swT) and symbolic visibly pushdown automata (sw-VPA) are introduced.

Based on these concepts, the paper introduces a variety of constructions.
The first one is a Bar-Hillel Perles Shamir construction for a given swT and a given sWA.  The second one performs the closure of two sw-VPA under the semiring operations.  The third one computes, for a given sw-VPA, the best word with respect to the natural order of the underlying semiring.

Finally, the paper introduces the framework of Symbolic Weighted Parsing, which, given
- a word from some input alphabet,
- an sw-VPA over some target alphabet, and
- an swT mapping words from the input alphabet to the internal symbols of the sw-VPA's alphabet,
  aims to compute a nested word which minimizes both the weight assigned to it by the sw-VPA and the distance to the input word (which is computed by the swT).  The authors show that this problem can be solved in polynomial time by combining the three constructions introduced earlier.  Moreover, they
  motivate their work by the example of the automatic transcription of music recordings into music scores.

- [ ] The formalism of symbolic weighted automata is not original to the paper.  It was already introduced by Herrmann and Vogler (2016) and later revised by Herrmann (2020) under the name of weighted symbolic automata with data storage.  This literature subsumes swA (by choosing the trivial storage), swT (since transducers can be understood as particular weighted automata), and sw-VPA, for which the data storage VP was defined.  Moreover, the earlier work is more general, since it allows unital valuation monoids (rather than just semirings) as weight structures.  They authors of the present paper should refer to the earlier publications and clearly distinguish between adopted concepts and their own work.

- [ ] Moreover, the authors claim that their framework is a generalization of previous approaches to weighted parsing, in the sense that it allows infinite input alphabets.  However, some of the previous approaches allowed more general weight structures than just semirings, so their are **incomparable** to the present paper.

@@

I enjoyed the running example of automatic music transcription which serves to illustrate every introduced concept and brings a different domain into consideration.  The overall impression of the paper is spoiled by many careless mistakes, such as formulas sticking out into the page margin (see below for a list).

Overall, I think that the paper cannot be published in its present form because the introduction of symbolic weighted automata without reference to the original literature could be seen as plagiarism.  I think, however, that the original work presented in the paper can be of interest to the scientific community.  This is why I opt to weakly reject the paper.  In order for the paper to be published, its focus should be shifted from the theory of symbolic weighted automata to the framework of symbolic weighted parsing.

In particular, the authors could spend fewer pages repeating already established
concepts from the literature and integrate Appendix D into the main paper.

REMAINS TO DO :
references :
- [ ] 75: maybe cite Parsing as intersection by Nederhof and Satta (2003)
- [ ] 126: you should cite Knuth's generalization of Dijkstra's algorithm for superiority, he defines the notion for functions of arbitrary arity, so not just semirings (but multioperator monoids); you should give an example for superiority in the semiring notation (with $\otimes$)
Moreover, the `corresponds' is wrong, since superiority generalizes non-negative edge weights
- [ ] PS: Knuth's definition of superiority includes monotonicity
- [ ] 143: Lemma 4 is Lemma 3 in [21]
- [ ] 195: references: there is earlier research on symbolic automata, e.g. Veanes (2013)
- [x]  Ref [22] and [23] both seem to refer to the same work by Mohri

- [ ] 51--53: the jump from automata to grammars is uneasy and not really necessary, as the paper mainly deals with automata
- [ ] 57: weighted automata don't have ASTs, but runs
- [x] 60: other approaches use multioperator monoids or valuation monoids, so `at minima a semiring' is wrong
- [ ] 116: $\oplus$ `combines two values into a single one' as well (in fact, every   binary operation does)
- [ ] 136: what implies?
- [x] 153: quantify $x$ and the family ($y_i$) for $i ∈ ℕ$
- [ ] 155--156: alphabets are usually finite and non-empty sets
- [ ] 159: denoted by; also it seems like $\bar\Phi$ is a ($\Sigma \cup \Sigma \times \Delta$)-indexed family, why don't you introduce it like this
- [ ] 161--171: use an itemize environment 
- [ ] 162--165: I think these should also hold for $\Delta$, why don't you write this explicitly?
- [ ] 188: the definition of $\bigoplus_\Delta$ can be seen to be implicit.  Please fully quantify the alphabets of a label theory
- [ ] 208: What does $T$ compute?
- [ ] 219: resp.\@
- [ ] 220--221: you mean that a term CONTAINING $w_{ij}(…)$ equal to 0 is ignored
- [ ] 238: text in the margin, also it is not clear whether the if refers to the entire line or just the right definition
- [ ] 284: $x$ is a variable, so it should be typeset in math mode
- [ ] 291: I'd at least say once that $\Delta_i$, $\Delta_c$, and $\Delta_r$ are pairwise disjoint (or explain the symbol)
- [ ] 297: the extension here is not as in Section 3, there, the different function hat at least similar types
- [ ] 299: every line expands into the margin; moreover, in the rightmost equation of line three, in the application of $w_c$, $p'$ and $q'$ are swapped
- [ ] 316: equation extends into margin
- [ ] 331: I think the application of $w_c$ is wrong (same with $w_r$ and $w_i$ later), shouldn't the : be a comma and what is q in the middle?
- [ ] 336: how are states (which are in $Q$) pushed onto the stack if $\Gamma = \Delta_c \times P$?
- [ ] 339: what are $j$ and $c$, do you mean $i$ and $d$?
- [ ] 341: shouldn't there be a transition for returning from a measure?
- [ ] 348: for?  do you mean accepted by?  but the language of an swA isn't defined either
- [ ] 354: readers may have an easier time seeing this argument if you say that $S$ is extremal.  You should say in the preliminaries that S is extremal if and only if $\leq_\oplus$ is total.
- [ ] 371: How is it ensured that the symbol $<c,p>$ isn't popped and pushed again later during the computation?
- [x] 376: I do not understand the and at termination, and its correctness part.  What do you want to express?
- [ ] 379: Almost all update equations need to compute infinite sums.  Don't you think that the assumption of $\bar\Phi$ being effective is pretty strong and gives your the result `for free'?  I think you should at least elaborate on this and say to what degree your effective label theory is a generalization of the decidable label theory of unweighted symbolic automata.
- [ ] 629: typical references for regular tree grammars are Brainerd (1969) 
- [ ] ​         and  Gecseg and Steinby (1984)
- [ ] 654: an intuition for the $\bar q$ would have made understanding the construction far easier

@@

- [x] 366: be popPED
- [ ] 371: How is it ensured that the symbol $<c,p>$ isn't popped and pushed again later during the computation?
- [x] 375: converge (singular)
- [x] 376: I do not understand the and at termination, and its correctness part.  What do you want to express?

@@

- [x] 650: missing period after function
- [x] 652: I think $\bar w$ should be $\bar w'$
- [ ] 654: an intuition for the $\bar q$ would have made understanding the construction far easier

Original literature:

- [ ] Herrmann and Vogler (2016): L. Herrmann & H. Vogler (2016): Weighted Symbolic Automata with Data Storage. In: Developments in Language Theory, Springer, pp. 203–215, doi:10.1007/978-3-662-53132-7 17.

- [ ] Herrmann (2020): L. Herrmann (2016): Weighted Automata with Storage. PhD thesis. Technische Universität Dresden, 2020, urn:nbn:de:bsz:14-qucosa2-740685

@@

The contributions of this paper are extending transducers and automata to handle symbolic inputs and to output weights in a semiring instead of Boolean values. The paper also gives procedures for computing minimum weights for given inputs and to compute witnesses for these minimum weights, which will be helpful to construct syntax trees. The definitions have been extended from the respective symbolic and weighted models. The technical details are mostly well written and complemented with intuitive explanations using a running example. However, for now, I am still giving weak accept instead of accept, since I am having difficulty understading a few points. See the last two comments below.

- [ ] Line 209:  "T is based on an intermediate function ...": should this be "The semantics of $T$ is based on an intermediate function ..."?

- [x] Line 281: "artitioned into three" -> "partitioned into three"

- [x] Last line of algorithm 1: What exactly is meant by "update $d_⊥$ with $<q_1,q_2>$"? Does it mean update the image of $<q_1,q_2>$ under $d_⊥$ with the new value as computed in Figure 3? Write this clearly.

Figure 3: This figure is supposed to compute $<q_1,q_2>$. 
- [x] First of all, it is not clear what is meant by "compute $<q_1,q_2>$"; I am guessing, as I wrote in the comment above that the computed quantity is the image of $<q_1,q_2>$ under $d_⊥$. However, even this doesn't make sense; there are some series of equantions written, for $d_\top(q_1,p,q_3)$ (not for $d_\top(q_1,p,q_2)$. 
- [x] Even in this equation, what is $q_2$? Do we take the minimum (wrt $\oplus$) over all $q_2$? 
- [x] The second line says $d_\bot(q_1,p,q_3)$, which doesn't make sense because $d_⊥$ takes two arguments, not three. 
- [x] There are two equations for $d_\top(q_1,p,q_3)$ and one for $d_\top(q_0,p,q_3)$. How are these related? It is very confusing what is being computed here and how. Please update this to make it clear.

@@

- [ ] l. 434: $swM$??

- [x] l. 435: "offline" -> "works offline"

- [x] l. 437: extraneous comma after "such as"

 References:
- [x]  Ref [22] and [23] both seem to refer to the same work by Mohri

### 2021-09-02 introduction.tex
1 passe modifs suivant certaines remarques des reviwers

Other extensions of language models  %(automata and grammars)
help in dealing with non-determinism by computing weight values.
With an ambiguous grammar, there may exist several derivations
(\emph{abstract syntax trees} -- AST) % \ie the result of an analyze.
yielding one input word. % structuring a word,
The association of one weight value %in semiring domain
to each AST permits to select a best one (or $n$ bests). % a fixed number of bests
% = ...a ranking of ASTs
%This is roughly the principle of \emph{weighted parsing} approaches
\florent{WARNING: \cite{MorbitzVogler19weighted-parsing} much is more general that weighted parsing}
In \emph{weighted language models}~\cite{Goodman99SemiringParsing,Nederhof03weightedParsing,MorbitzVogler19weighted-parsing},
like \eg probabilistic context-free grammars % (CFG),
and weighted automata (\WA) \cite{Droste09handbook},
a weight is associated to each transition rule, % production rule
and the rule's weights can be combined with an
associative product operator~$\otimes$ to yield the weight of an AST.
A second operator~$\oplus$
is moreover used to resolve the ambiguity raised by the existence
of several (in general exponentially many) AST
associated to a given input word.
Typically, $\oplus$  selects the best of two weight values.
%Intuitively,~$\oplus$ selects, or ranking, the syntax trees.
The weight domain, equipped with these two operators is, at minima,
a \emph{semiring} %$\Semiring$
where $\oplus$ can be extended to infinite sums,
%\cite{Eilenberg74automata}
such as the Viterbi semiring and the tropical min-plus algebra% % see Figure~\ref{fig:semirings}.
%of domain $\mathbb{R}^+ \cup \{ +\infty\}$,
%where $\oplus$ is min and $\otimes$ is plus .
%by ranking
%making the weight domain a semiring.
%Some efficient specialized parsing algorithms~\cite{Huang05kbest} have been proposed in this context
%% models represented as hypergraphs \cite{Huang05kbest}
%in order to compute the $n$ best syntax trees of a given input word without having to enumerate them all.
%Generally based on dynamic programming, these algorithms rely on
%additional algebraic properties of~$\Semiring$.
%-- see \eg~\cite{Huang05kbest} for some NLP applications.
%The extraction of $n$ best list is useful
%the problem: quantitative parsing or symbolic parsing
%of parsing of words over infinite input alphabet.

@@

The framework relies on several language models:
symbolic-weighted automata (\SWA),
transducers (\SWT), and pushdown automata
with a visibility restriction~\cite{AlurMadhusudan09nested} (\SWVPA).
A \SWT defines a distance $T(s, t)$ between finite words $s$ and $t$
over infinite alphabets. % following~\cite{Mohri03EDWA}.
%\wrt an edit distance
A  \SWVPA operates sequentially on \emph{nested words}~\cite{AlurMadhusudan09nested},
structured with markup symbols (parentheses) and describing linearizations of trees.
A \SWVPA $A$ associates a weight value $A(t)$ % \in \Semiring$
to a given nested word $t$, which is itsef the linearization of a weighted AST. %representing a parse tree.
%
Then, given an input word $s$, the \emph{SW-parsing} problem aims at
finding $t$ minimizing
$T(s, t) \otimes A(t)$, called the distance between $s$ and $A$ in~\cite{Mohri03EDWA},
\wrt the ranking defined by $\oplus$. Like weighted-parsing
methods~\cite{Goodman99SemiringParsing,Nederhof03weightedParsing,MorbitzVogler19weighted-parsing},
\florent{WARNING: \cite{MorbitzVogler19weighted-parsing} much is more general that weighted parsing}
our approach proceeds in two steps.
The first step is an intersection
(Bar-Hillel construction~\cite{GruneJacobs08parsing})
\florent{chap. intersection in~\cite{GruneJacobs08parsing}}
where, given a \SWT $T$, a \SWVPA $A$, and an input word $s$,
a \SWVPA $B$ %$A_{T, s}$
is built, such that for all~$t$,
$B(t) = T(s, t) \otimes A(t)$. % $A_{T, s}(t) = T(s, t) \otimes A(t)$.
In the second step, a best AST $t$ is found by applying to $B$ %$A_{T, s}$
a best search algorithm similar to the shortest distance
in graphs~\cite{Mohri02semiring,Huang05kbest}.
%In expressiveness, they are equivalent to weighted CFG.
%and can be used in a general approach for parsing over infinite input alphabets.
%
%Let $A$ be a \SWVPA, associating $A(w) \in \Semiring$
%to a given a nested word $w$ (representing a parse tree),
%and let a \SWT compute a distance $d$, in $\Semiring$,
%between 2 strings over respectively an infinite input alphabet and the
%same (infinite) alphabet of $A$.
%Then, the problem of Symbolic Weighted Parsing is,
%given an input string $s$, to find a nested word $w$ minimizing
%(according to the ranking defined by $\oplus$)
%the distance $d(s, w) \otimes A(w)$ between $s$ and $A$,
%as defined in~\cite{Mohri03EDWA}.

>>>>

Other extensions of language models  %(automata and grammars)
help in dealing with non-determinism by computing weight values.
With an ambiguous grammar, there may exist several derivations
(\emph{abstract syntax trees} -- AST) % \ie the result of an analyze.
yielding one input word. % structuring a word,
The association of one weight value %in semiring domain
to each AST permits to select a best one (or $n$ bests). % a fixed number of bests
% = ...a ranking of ASTs
%This is roughly the principle of \emph{weighted parsing} approaches
\florent{WARNING: \cite{MorbitzVogler19weighted-parsing} much is more general that weighted parsing}
In \emph{weighted language models}~\cite{Goodman99SemiringParsing,Nederhof03weightedParsing,MorbitzVogler19weighted-parsing},
like \eg probabilistic context-free grammars % (CFG),
and weighted automata (\WA) \cite{Droste09handbook},
a weight is associated to each transition rule, % production rule
and the rule's weights can be combined with an
associative product operator~$\otimes$ to yield the weight of an AST.
A second operator~$\oplus$
is moreover used to resolve the ambiguity raised by the existence
of several (in general exponentially many) AST
associated to a given input word.
Typically, $\oplus$  selects the best of two weight values.
%Intuitively,~$\oplus$ selects, or ranking, the syntax trees.
The weight domain, equipped with these two operators is typically 
a \emph{semiring} %$\Semiring$
where $\oplus$ can be extended to infinite sums,
%\cite{Eilenberg74automata}
such as the Viterbi semiring and the tropical min-plus algebra% % see Figure~\ref{fig:semirings}.
%of domain $\mathbb{R}^+ \cup \{ +\infty\}$,
%where $\oplus$ is min and $\otimes$ is plus .
%by ranking
%making the weight domain a semiring.
%Some efficient specialized parsing algorithms~\cite{Huang05kbest} have been proposed in this context
%% models represented as hypergraphs \cite{Huang05kbest}
%in order to compute the $n$ best syntax trees of a given input word without having to enumerate them all.
%Generally based on dynamic programming, these algorithms rely on
%additional algebraic properties of~$\Semiring$.
%-- see \eg~\cite{Huang05kbest} for some NLP applications.
%The extraction of $n$ best list is useful
%the problem: quantitative parsing or symbolic parsing
%of parsing of words over infinite input alphabet.

@@

The framework relies on several language models:
symbolic-weighted automata (\SWA),
transducers (\SWT), and pushdown automata
with a visibility restriction~\cite{AlurMadhusudan09nested} (\SWVPA).
A \SWT defines a distance $T(s, t)$ between finite words $s$ and $t$
over infinite alphabets. % following~\cite{Mohri03ijfcs}.
%\wrt an edit distance
A  \SWVPA operates sequentially on \emph{nested words}~\cite{AlurMadhusudan09nested},
structured with markup symbols (parentheses) and describing linearizations of trees.
A \SWVPA $A$ associates a weight value $A(t)$ % \in \Semiring$
to a given nested word $t$, which is itsef the linearization of a weighted AST. %representing a parse tree.
%
Then, given an input word $s$, the \emph{SW-parsing} problem aims at
finding $t$ minimizing
$T(s, t) \otimes A(t)$, called the distance between $s$ and $A$ in~\cite{Mohri03ijfcs},
\wrt the ranking defined by $\oplus$. Like weighted-parsing
methods~\cite{Goodman99SemiringParsing,Nederhof03weightedParsing,MorbitzVogler19weighted-parsing},
\florent{WARNING: \cite{MorbitzVogler19weighted-parsing} much is more general that weighted parsing}
our approach proceeds in two steps.
The first step is an intersection
(Bar-Hillel construction~\cite{GruneJacobs08parsing})
\florent{chap. intersection in~\cite{GruneJacobs08parsing}}
where, given a \SWT $T$, a \SWVPA $A$, and an input word $s$,
a \SWVPA $B$ %$A_{T, s}$
is built, such that for all~$t$,
$B(t) = T(s, t) \otimes A(t)$. % $A_{T, s}(t) = T(s, t) \otimes A(t)$.
In the second step, a best AST $t$ is found by applying to $B$ %$A_{T, s}$
a best search algorithm similar to the shortest distance
in graphs~\cite{Mohri02semiring,Huang05kbest}.
%In expressiveness, they are equivalent to weighted CFG.
%and can be used in a general approach for parsing over infinite input alphabets.
%
%Let $A$ be a \SWVPA, associating $A(w) \in \Semiring$
%to a given a nested word $w$ (representing a parse tree),
%and let a \SWT compute a distance $d$, in $\Semiring$,
%between 2 strings over respectively an infinite input alphabet and the
%same (infinite) alphabet of $A$.
%Then, the problem of Symbolic Weighted Parsing is,
%given an input string $s$, to find a nested word $w$ minimizing
%(according to the ranking defined by $\oplus$)
%the distance $d(s, w) \otimes A(w)$ between $s$ and $A$,
%as defined in~\cite{Mohri03ijfcs}.

### 2021-09-02 main-V0.tex
comment versions
1 passe modifs suivant certaines remarques des reviwers

% old version

@@

over an infinite alphabet, following~\cite{Mohri03EDWA}.

@@

-- this value is called the distance between $s$ and $A$ in~\cite{Mohri03EDWA}.

@@

%as defined in~\cite{Mohri03EDWA}.

@@

We follow the approach of~\cite{Mohri03EDWA} for the computation of distances
between words and languages, with weighted transducers, 
extending it to infinite alphabets.
% with models of symbolic weighted automata and transducers. 
%
The models introduced in this section generalize 
weighted automata and transducers~\cite{Droste09handbook} 
%over finite alphabets, see  e.g.~\cite{Mohri03EDWA}, 
by labeling each transition with a weight function that takes the 
input and output symbols as parameters, instead of a simple weight value.
These functions are similar to the guards of symbolic automata~\cite{dAntoniVeanes17CAV,dAntoni21CACM},
but they can return values in an arbitrary semiring, 
where the latter guards are restricted to the Boolean semiring.

@@

\noindent 
Therefore, it is the problem of optimizing a measure 
called the \emph{edit-distance between $s$ and $A$} in~\cite{Mohri03EDWA}.
%
The input language can also be expressed as a \SWTA, or, 
as a particular case, as a weighted context-free grammar, 
converted in turn into a \SWVPA following Lemma~\ref{lem:SWTA}.
%
In the case of finite alphabets, 
the problem of searching, in a WTA language, 
for the best parse tree for a given,  
sometimes referred as~\emph{weighted parsing}
(see \cite{Goodman99SemiringParsing,MorbitzVogler19weighted-parsing} **more general problems**)
is a particular case of SW parsing.
%
Indeed, it corresponds to the case where $T$
accepts only the pairs $\<s, t>$ such that 
$s$ is the projection of $t$ on $\Omegai$. 
This can be done with a single state $q$ and 
with transition rules of the form:
\begin{description}
\item[] $\wei(q, \epsilon, a, q) = \one$ for all $a \in \Omegac \cup \Omegar$,
\item[] $\wei(q, a, a, q) = \one$ for all $a \in \Omegai$,
\item[] $\wei(q, a, b, q) = \zero$ for all $a, b \in \Omegai$, $a \neq b$.
\end{description}

@@

%\subsection{Distance between words or languages}
...algebraic definition of edit-distance of Mohri, in \cite{Mohri03EDWA}
% Mehryar Mohri 
% Edit-distance of weighted automata: General definitions and algorithms
% International Journal of Foundations of Computer Science 14.06 (2003): 957-982.
distance $d$ over $\Sigma^* \times \Sigma^*$ 
into a semiring  $\Semiring = ( \Semiring, \oplus, \zero, \otimes, \one)$.

>>>>

%
% initial version 
% 
%

@@

over an infinite alphabet, following~\cite{Mohri03ijfcs}.

@@

-- this value is called the distance between $s$ and $A$ in~\cite{Mohri03ijfcs}.

@@

%as defined in~\cite{Mohri03ijfcs}.

@@

We follow the approach of~\cite{Mohri03ijfcs} for the computation of distances
between words and languages, with weighted transducers, 
extending it to infinite alphabets.
% with models of symbolic weighted automata and transducers. 
%
The models introduced in this section generalize 
weighted automata and transducers~\cite{Droste09handbook} 
%over finite alphabets, see  e.g.~\cite{Mohri03ijfcs}, 
by labeling each transition with a weight function that takes the 
input and output symbols as parameters, instead of a simple weight value.
These functions are similar to the guards of symbolic automata~\cite{dAntoniVeanes17CAV,dAntoni21CACM},
but they can return values in an arbitrary semiring, 
where the latter guards are restricted to the Boolean semiring.

@@

\noindent 
Therefore, it is the problem of optimizing a measure 
called the \emph{edit-distance between $s$ and $A$} in~\cite{Mohri03ijfcs}.
%
The input language can also be expressed as a \SWTA, or, 
as a particular case, as a weighted context-free grammar, 
converted in turn into a \SWVPA following Lemma~\ref{lem:SWTA}.
%
In the case of finite alphabets, 
the problem of searching, in a WTA language, 
for the best parse tree for a given,  
sometimes referred as~\emph{weighted parsing}
(see \cite{Goodman99SemiringParsing,MorbitzVogler19weighted-parsing} **more general problems**)
is a particular case of SW parsing.
%
Indeed, it corresponds to the case where $T$
accepts only the pairs $\<s, t>$ such that 
$s$ is the projection of $t$ on $\Omegai$. 
This can be done with a single state $q$ and 
with transition rules of the form:
\begin{description}
\item[] $\wei(q, \epsilon, a, q) = \one$ for all $a \in \Omegac \cup \Omegar$,
\item[] $\wei(q, a, a, q) = \one$ for all $a \in \Omegai$,
\item[] $\wei(q, a, b, q) = \zero$ for all $a, b \in \Omegai$, $a \neq b$.
\end{description}

@@

%\subsection{Distance between words or languages}
...algebraic definition of edit-distance of Mohri, in \cite{Mohri03ijfcs}
% Mehryar Mohri 
% Edit-distance of weighted automata: General definitions and algorithms
% International Journal of Foundations of Computer Science 14.06 (2003): 957-982.
distance $d$ over $\Sigma^* \times \Sigma^*$ 
into a semiring  $\Semiring = ( \Semiring, \oplus, \zero, \otimes, \one)$.

### 2021-09-02 main-V1.tex
comment versions
V1: file descr. in comment
1 passe modifs suivant certaines remarques des reviwers

@@

We follow the approach of~\cite{Mohri03EDWA} for the computation of distances,
between words and languages, using weighted transducers, 
and extend it to infinite alphabets.
% with models of symbolic weighted automata and transducers. 
%
The models introduced in this section generalize 
weighted automata and transducers~\cite{Droste09handbook} 
%over finite alphabets, see  e.g.~\cite{Mohri03EDWA}, 
by labelling each transition with a weight function (instead of a simple weight value), 
that takes the input and output symbols as parameters. 
These functions are similar to the guards of symbolic automata~\cite{dAntoniVeanes17CAV,dAntoni21CACM},
but they can return values in an generic semiring, 
whereas the latter guards are restricted to the Boolean semiring.

>>>>

%
% transducers and automata with epsilon transitions
%

@@

We follow the approach of~\cite{Mohri03ijfcs} for the computation of distances,
between words and languages, using weighted transducers, 
and extend it to infinite alphabets.
% with models of symbolic weighted automata and transducers. 
%
The models introduced in this section generalize 
weighted automata and transducers~\cite{Droste09handbook} 
%over finite alphabets, see  e.g.~\cite{Mohri03ijfcs}, 
by labelling each transition with a weight function (instead of a simple weight value), 
that takes the input and output symbols as parameters. 
These functions are similar to the guards of symbolic automata~\cite{dAntoniVeanes17CAV,dAntoni21CACM},
but they can return values in an generic semiring, 
whereas the latter guards are restricted to the Boolean semiring.
